\chapter*{\centerline{Acknowledgments}\vspace{-3cm}}
\markboth{\MakeUppercase{Acknowledgments}}{}
\iftoggle{fulltoc}{
  \addcontentsline{toc}{chapter}{Acknowledgments}
}{}
My time at the University of Rochester was impacted by so many people, but as I finish writing 
this 50 page summary of the past year of research, I am reminded of those who made it truly special.

First and foremost I want to thank the Department of Physics and Astronomy for providing a nurturing 
environment over the past four years, in and out of the COVID-19 pandemic. I commonly refer to B\&L and the POA as my second home,
and without the efforts of each and every professor, administrator, and faculty member, my experience would simply 
have not been the same. 

I would also like to thank Professor Segev BenZvi for his patience and intuition during the past year. 
He has been an absolute pleasure to work with, both in person and online, and he continues to fascinate 
me with the passion he brings to every meeting. He has shown me what true dedication to a field is, 
and one day I hope to impact someones life as he has impacted mine. 

Professor Kelly Douglass was the first professor at the University of Rochester I had the 
pleasure of meeting, providing me with words of wisdom after the first 
college lecture I ever attended  (during a tour of the school). She continued to offer 
insight and advice throughout my four years studying physics and astronomy, and she has been the 
image of a fair, caring professor ever since I first walked into her classroom. 

Thank you to my father and mother, Salvatore and Gigi LaBarca, for their ongoing and unending support of my work and my sisters,
Marisa and Carrie, who always find a way to make me laugh and strive for greatness. Thank you to my friends on campus and at home
who deal with my egregiously packed school-music-ultimate schedule, and my peers, too numerous to 
mention by name, who shared scientific advice and late nights together. Finally, thank you to Grace, for all of
our astronomy discussions, but more importantly, for reminding me that there are always 5 minutes 
in a day to enjoy the company of those you love. 